SoK: Transparent Dishonesty: front-running attacks on Blockchain.

### 2019-02-19 frontrunning/Latex/sections/paper.tex
[frontrunning] Fix some typos and conclusion

First-in-first-out (FIFO) is generally not possible on a distributed network because transactions can reach different nodes in a different order. While the network could theoretically form a consensus based on locally observed FIFO, this would increase the rate of orphaned blocks, as well as adding complexity to the protocol. A trusted third party can be used to assign sequential numbers to transactions (and sign them), but this is contrary to blockchain's core innovation of distributed trust. None the less, some exchanges do centralize time-sensitive functionalities (\eg  \textit{EtherDelta} and \textit{0xProject}) in off-chain order books~\cite{warren20170x,0xfrontrunning:online}.

@@

A DApp includes the following components: (1) the code of the DApp, (2) the current state of the DApp, (3) the name of the function being invoked, (4) the parameters supplied to the function, (5) the address of the contract the function is being invoked on, and (6) the identity of the sender. Confidentiality applied to a DApp could mean different levels of protection for each of these. For front-running, function calls (3,4) are the most important, however, function calls could be inferred from state changes (2). Hawk~\cite{kosba2016hawk} and Ekiden~\cite{cheng2018ekiden} are examples of (2,3,4)-confidentiality (with limitations we are glossing over).

@@

%Shayan -> TODO: Jeremy: the following probably needs some rewrite to focus on the solution rather than the issue.
Another example in the design of ERC20 standard~\cite{erc20}, is on the allowance functionality. \textit{approve()} function in the specification allows a second entity to be able to spend N tokens from the sender's balance. In order to change the allowance, sender must send a transaction to set the new allowance value. Using the insertion attack, attacker could front-run the new allowance transaction and spend the old value before the new value is set~\cite{blockchainProjectAllowanceAttack,erc20GithubIssue}, and then additionally spend the new amount at a later time. Solutions such as \textit{decreaseApproval()}/\textit{increaseApproval()} were added in updated implementations.

@@

Front-running is a pervasive issue in Ethereum DApps. While some DApp-level application logic could be built to mitigate these attacks, its ubiquity across different DApp categories suggests mitigations at the blockchain-level would perhaps be more effective. We highlight this as an important research area.

>>>>

First-in-first-out (FIFO) is generally not possible on a distributed network because transactions can reach different nodes in a different order. While the network could theoretically form a consensus based on locally observed FIFO, this would increase the rate of orphaned blocks, as well as adding complexity to the protocol. A trusted third party can be used to assign sequential numbers to transactions (and sign them), but this is contrary to blockchain's core innovation of distributed trust. Nonetheless, some exchanges do centralize time-sensitive functionalities (\eg  \textit{EtherDelta} and \textit{0xProject}) in off-chain order books~\cite{warren20170x,0xfrontrunning:online}.

@@

A DApp interaction includes the following components: (1) the code of the DApp, (2) the current state of the DApp, (3) the name of the function being invoked, (4) the parameters supplied to the function, (5) the address of the contract the function is being invoked on, and (6) the identity of the sender. Confidentiality applied to a DApp could mean different levels of protection for each of these. For front-running, function calls (3,4) are the most important, however, function calls could be inferred from state changes (2). Hawk~\cite{kosba2016hawk} and Ekiden~\cite{cheng2018ekiden} are examples of (2,3,4)-confidentiality (with limitations we are glossing over).

@@

%Shayan -> TODO: Jeremy: the following probably needs some rewrite to focus on the solution rather than the issue.
Another example in the design of ERC20 standard~\cite{erc20} is the allowance functionality. \textit{approve()} function in the specification allows a second entity to be able to spend N tokens from the sender's balance. In order to change the allowance, sender must send a transaction to set the new allowance value. Using the insertion attack, attacker could front-run the new allowance transaction and spend the old value before the new value is set~\cite{blockchainProjectAllowanceAttack,erc20GithubIssue}, and then additionally spend the new amount at a later time. Solutions such as \textit{decreaseApproval()}/\textit{increaseApproval()} were added in updated implementations.

@@

Front-running is a pervasive issue in Ethereum DApps. DApp developers don't necessarily have the mindset to design DApps with front-running in mind. This is an attempt to bring forward the subject and make more awareness of these type of attacks. While some DApp-level application logic could be built to mitigate these attacks, its ubiquity across different DApp categories suggests mitigations at the blockchain-level would perhaps be more effective. We highlight this as an important research area.
